Why Donors Donate?

### 2020-08-31 analysis/05_market_simulator.Rmd
Added commented to explain plotly code

    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])
#add step to matrix multiply the persona reactive element to the persona data and the public_political beta table.

  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)

  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])

  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)

  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))

    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])

  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)

  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))

  data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
            ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2, ai_rate2, gp_rate2, ox_rate2, rc_rate2,
            ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3, ai_rate3, gp_rate3, ox_rate3, rc_rate3)

  df <- as.data.frame(matrix(data, 24, 1))

  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% filter(Type == "Market Share") %>%
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})

>>>>

  # Persona 1 
    p_beta1 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,3])

  # Expected Utility
  ai_exp_util1 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta1)),2)

  # Market Share
  ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
  rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

  # Persona 2
    p_beta2 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,4])

  # Expected Utility
  ai_exp_util2 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta2)),2)
  gp_exp_util2 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta2)),2)
  ox_exp_util2 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta2)),2)
  rc_exp_util2 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta2)),2)

  # Market Share
  ai_rate2 <- round(100 * ai_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  gp_rate2 <- round(100 * gp_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  ox_rate2 <- round(100 * ox_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))
  rc_rate2 <- round(100 * rc_exp_util2/sum(ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2))

  # Persona 3
    p_beta3 <- as.matrix(public_political_social_charity_demo) %*% as.matrix(per_choice[,5])

  # Expected Utility
  ai_exp_util3 <- round(exp(t(org_choice[, 3]) %*% as.matrix(p_beta3)),2)
  gp_exp_util3 <- round(exp(t(org_choice[, 4]) %*% as.matrix(p_beta3)),2)
  ox_exp_util3 <- round(exp(t(org_choice[, 5]) %*% as.matrix(p_beta3)),2)
  rc_exp_util3 <- round(exp(t(org_choice[, 6]) %*% as.matrix(p_beta3)),2)

  # Market Share
  ai_rate3 <- round(100 * ai_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  gp_rate3 <- round(100 * gp_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  ox_rate3 <- round(100 * ox_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))
  rc_rate3 <- round(100 * rc_exp_util3/sum(ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3))

  # Data for Plotly
  data <- c(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1, ai_rate1, gp_rate1, ox_rate1, rc_rate1, 
            ai_exp_util2, gp_exp_util2, ox_exp_util2, rc_exp_util2, ai_rate2, gp_rate2, ox_rate2, rc_rate2,
            ai_exp_util3, gp_exp_util3, ox_exp_util3, rc_exp_util3, ai_rate3, gp_rate3, ox_rate3, rc_rate3)

  # Empty dataframe
  df <- as.data.frame(matrix(data, 24, 1))

  # Organization name inputs
  df[,2] <- c(input$ai_id, input$gp_id, input$ox_id, input$rc_id)
  # Type of value
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  # Persona name inputs
  df[,4] <- c(rep(input$p1_id,8), rep(input$p2_id, 8), rep(input$p3_id, 8))

  # Rename columns
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

  ggplotly(df %>% 
             # Only care about the Market Share right now
             filter(Type == "Market Share") %>% 
             # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
             mutate(
               Organization = factor(Organization, levels = c(input$ai_id, input$gp_id, input$ox_id, input$rc_id), ordered = TRUE),
               Persona = factor(Persona, levels = c(input$p1_id, input$p2_id, input$p3_id), ordered = TRUE)) %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="", y = "Market Share") + 
             scale_fill_manual(values = c( "#FFC30B", "#28a153", "#c23838")) +
             theme(legend.position = "right",
                   panel.background = element_blank(),
                   panel.grid.major.y = element_line(color = "#D3D3D3"))
    )
})
